Modeling tabular icebergs coupled to an ocean model

### 2017-02-16 Icebergs_only.tex
More changes to iceberg only version

 \end{article}
 \clearpage 
\section{Extra Figure:}
 \clearpage 
\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/three_melt_melt_m_per_year.png}
\caption{ {Melt rate 30 days after calving for simulations using melt rates derived using (a) three equation model, (b) icebergs drift parametrization, (c) a mixture between the two (as described in Section 2.5.}}
\end{center}
\label{fig:threemelt}
\end{figure}
 \clearpage

>>>>

 \end{article}
 \clearpage 
\section{Extra Figure:}
 \clearpage 
\begin{figure}
\begin{center}
\includegraphics[width=0.99\textwidth]{/Users/alon/Desktop/files/Icebergs_clusters/Towards_Publication/Tech_paper/Github_stuff/Tech-paper/Figures/three_melt_melt_m_per_year.png}
\caption{ {Melt rate 30 days after calving for simulations using melt rates derived using (a) three equation model, (b) icebergs drift parametrization, (c) a mixture between the two (as described in Section 2.5.)}}
\end{center}
\label{fig:threemelt}
\end{figure}
 \clearpage
